---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# htmlreportR

<!-- badges: start -->
[![R-CMD-check](https://github.com/AEstebanMar/htmlreportR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AEstebanMar/htmlreportR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

htmlreportR has not been built from scratch. It is based on its Python equivalent and sister project, available at <https://pypi.org/project/py-report-html/> for a Python equivalent.

## Installation

Standard installation:

``` r
install.packages("htmlreportR")
```

You can install the development version of htmlreportR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AEstebanMar/htmlreportR")
```

## Example

There are two use cases for htmlreportR: script mode and package mode.

### Script mode

Simply call the html_report.R script, distributed with this package. Simply
provide a comma-separated list of files and a template to render, and you're done!


```{r script_example, engine = 'bash', eval = FALSE}
./scripts/html_report.R -d data1.txt,data2.txt -t template.txt
```

### Library mode

If you wish to use htmlreportR directly from R, you can! Here's how:
```{r library_example, eval = FALSE}
library(htmlreportR)
container <- list(data1 = data_frame_1, data2 = data_frame_2,
                  additional_field = "You can include anything in the container
                  and it will be available in plotter$hash_vars")
plotter <- htmlReport$new(title_doc = "Your report title", 
                          container = container, tmp_folder = "tmp_lib",
                          src = "path/to/htmlreportR/scripts")
```

### Tutorial

In tests/demo\_examples you will find the launch.sh script. Execute it and it will generate three html files with examples on how to use our package. report.html and report\_compressed.html are the exact same, only that the second was compressed using our package's functionality. report\_lib.html is a showcase on how our package may be used in what we call "library" mode, which allows software developers to directly call htmlreportR functions instead of relying on our script.

The templates used to render these reports may be found in that same directory. They are template.txt for script mode and template\_lib.txt for library mode.

Happy reporting!
