---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# htmlreportR

<!-- badges: start -->
[![R-CMD-check](https://github.com/AEstebanMar/htmlreportR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/AEstebanMar/htmlreportR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Create compressed, interactive 'HTML' (Hypertext Markup Language) reports with embedded 'Python' code, custom 'JS' (JavaScript) and 'CSS' (Cascading Style Sheets), and wrappers for
  'CanvasXpress' plots, networks and more. Based on https://github.com/seoanezonjic/py_report_html, its sister project.
htmlreportR provides a streamlined, R-friendly way to build interactive HTML reports with custom JS and CSS import
capabilities. It also contains wrapper functions for R CanvasXpress, performing all the formatting heavy-lifting
so users can focus on the actual report.

htmlreportR has not been built from scratch. It is based on its Python equivalent and sister project, available at https://github.com/seoanezonjic/py_report_html for a Python equivalent.

## Installation

Standard installation:

``` r
install.packages("htmlreportR")
```

You can install the development version of htmlreportR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AEstebanMar/htmlreportR")
```

## Example

There are two use cases for htmlreportR: script mode and package mode.

### Script mode

Simply call the html_report.R script, distributed with this package. Simply
provide a comma-separated list of files and a template to render, and you're done!


```{r script_example, engine = 'bash', eval = FALSE}
./scripts/html_report.R -d data1.txt,data2.txt -t template.txt
```

### Library mode

If you wish to use htmlreportR directly from R, you can! Here's how:
```{r library_example, eval = FALSE}
library(htmlreportR)
container <- list(data1 = data_frame_1, data2 = data_frame_2,
                  additional_field = "You can include anything in the container
                  and it will be available in plotter$hash_vars")
plotter <- htmlReport$new(title_doc = "Your report title", 
                          container = container, tmp_folder = "tmp_lib",
                          src = "path/to/htmlreportR/scripts")
```
